Environmental factors affecting Galaxy Morphology

### 2014-07-27 Writeup/paper_v2.tex
more comments from rachel

@@

Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$. 
We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.

@@

While our method to find overdensities may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density. Refer to Figure~\ref{fig:comoving_densities}.
And the unclassified regions fall below or at least lie close to the 10\% margin.
In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.
%Refitting the model to our new sample is consistent with the previous assignment of overdensities.

@@

Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
However, our method of finding the value of $q$ is little more complicated. Briefly, we fit
two models to each image:
\begin{enumerate}
 \item a \sersic profile given by the expression 
       \begin{equation} 
    S = \Sigma_{1/2}\exp{\left( -k(R/R_{\text{eff}})^{1/n} -1 \right)},
       \end{equation}
       \item two \sersic component fits: de Vaucoulers bulge $(n=4)$ + exponential disc profile $(n=1)$,
\end{enumerate}
where \begin{align*} R^2 = & ((x-x_0)\cos\Phi+(y-y_0)\sin\Phi)^2  \\ & + ((y-y_0)\cos\Phi-(x-x_0)\sin\Phi)^2/q^2, \end{align*}
$R_{\text{eff}}$ is the half-light radius of the profile, $\Sigma_{1/2}$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
$\Phi$ is the profile rotation angle, $n$ is the \sersic index, $k$ is a $n$-dependent normalization factor and $q$ is the axis ratio of the elliptical isophotes,
which is the quantity of interest to us. We find the best-fit parameters \emph{simultaneously}, by minimizing the weighted
sum of the difference between the image and the PSF-convolved model. More details about the fit can be found in~\cite{Claire_Fits}.

>>>>

\rachel{I am a bit confused here.  Our initial strategy was as
  follows: use all galaxies with $F814W<23.5$ or 25.2 to define a
  redshift distribution that we fit with one of our functional forms,
  use that to define overdensities, and then later when we're checking
  the variation of properties with redshift, we restrict to
  volume-limited subsamples.  But here you seem to be volume-limiting
  as the first step, which is not really appropriate. The functional
  forms that people have derived for surveys are predicated on the
  assumption that they are flux-limited.  What is the justification
  for volume-limiting first?  if there is none, then we should not be
  doing it. And then this section will have 3 subsection: finding
  overdensities, estimating axis ratios, and volume limiting,
  where we need to explain the two choices (using $B$-band evolution
  and using no evolution).}

@@

Overdensity in a redshift bin is defined as the ratio of the difference between the value given by the histogram and the value predicted by the model to the latter: $\delta=(N-N_{\text{mod}})/N_{\text{mod}}$. 
We leave a 10\% margin of safety i.e. iff $\delta$ from both the fits is greater than $0.1$, then we call that redshift bin as an
overdense region whereas if $\delta$ from both the fits is less than $-0.1$, then we call that as an underdense region. Redshift bins with $-0.1 < \delta < 0.1$ are neither too overdense
nor too underdense and we call them as `unclassified regions'  and discard them from our analysis.{\bf Fig 4 - overdensities vs redshift bins}.
\rachel{Let's not discard them.  We should just treat them as
  ``environmentally neutral.''  You do after all show them on your plots.}

@@

\rachel{I think ``arbitrary'' is not the right word ot use in this
  paragraph.  It's obviously well-motivated in a general sense, and
  the question is whether it's robust or not.  Comparison with a more
  robust 3d method is what we use as validation to say that it's
  robust enough for our purposes.}
While our method to find overdensities may seem arbitrary, the overdense and underdense regions obtained by the above method have local average number density higher than the global average number density. Refer to Figure~\ref{fig:comoving_densities}.
And the unclassified regions fall below or at least lie close to the 10\% margin.
In computing comoving densities, we have chosen the following values for the $\Lambda$CDM parameters: $\Omega_m = 0.3, \Omega_\Lambda = 0.7 \text{ and } \Omega_k = 0$ with the Hubble parameter $h = 0.72$.
%Refitting the model to our new sample is consistent with the previous assignment of overdensities.

@@

Conversely, one could compute $\chi$ or $\epsilon$ for a galaxy, and obtain an effective, azimuthally averaged {\bf(?)} axis-ratio $q$. 
\rachel{No, that isn't possible because of the PSF.  One would have to
  use a PSF correction scheme.  Recommend removing much of the above discussion.}
However, our method of finding the value of $q$ is little more complicated. Briefly, we fit
two models to each image:
\begin{enumerate}
 \item a \sersic profile given by the expression 
       \begin{equation} 
    S = \Sigma_{1/2}\exp{\left( -k(R/R_{\text{eff}})^{1/n} -1 \right)},
       \end{equation}
       \item two \sersic component fits: de Vaucoulers bulge $(n=4)$ + exponential disc profile $(n=1)$,
\end{enumerate}
where \begin{align*} R^2 = & ((x-x_0)\cos\Phi+(y-y_0)\sin\Phi)^2  \\ & + ((y-y_0)\cos\Phi-(x-x_0)\sin\Phi)^2/q^2, \end{align*}
$R_{\text{eff}}$ is the half-light radius of the profile, $\Sigma_{1/2}$ is the surface brightness at $R=R_{\text{eff}}$, $(x_0,y_0)$ is the centroid of the image,
$\Phi$ is the profile rotation angle, $n$ is the \sersic index, $k$ is a $n$-dependent normalization factor and $q$ is the axis ratio of the elliptical isophotes,
which is the quantity of interest to us. We find the best-fit parameters \emph{simultaneously}, by minimizing the weighted
sum of the difference between the image and the PSF-convolved model. More details about the fit can be found in~\cite{Claire_Fits}.
